---
title: "Diet Treatments to Standard Lab Mice"
output: html_notebook
---

This is a practice experiment and data analysis using a simulated dataset of 10 standard lab mice. In this experiemnt, we observe the changes in mice weight between a control and a treatment of a change in diet for decrease in mass. 

In order to find the standard weight of lab mice, we used information from [The Jackson Laboratory](https://www.jax.org/jax-mice-and-services/strain-data-sheet-pages/body-weight-chart-000664). Since the information here shows ranges of mice weights depending on age and gender, we chose the weight of males at 6weeks of age. This specific mice has an average weight of 21.1g with a standard deviation of 1.5. We set the time between examination of the mice to be one week. In this case, we assume that mice weight has a normal distribution. 

In order to simulate the data, we separated the dataset by treatment groups, since they both have separate trends, and merge the data together into the full data. We start first by producing mouse weight data for the first timepoint, basing this sample in a normal distribution and to the information on mice weights we have. Then for the second time point, we use each weight point from the first time event and use a formula made based on the mice information we have to produce the point for each mouse. we do this repeatedly until we receive 4 timepoints for 5 mice for each treatment group dataset.

The following two datasets are of the control group (data1) and the treatment group (data2), separately simulated. In both datasets, time represents the observation time, with 0 being the start of the experiment, 1 being the first week into the experiment, and so on. id represents each individual mouse. weight is the weight of the mouse in grams, and treatment is the treatment group each mouse is in, with A being the control and B being the treatment.

```{r}
data1
```

```{r}
data2
```





By combining the two separate datasets and adding columns for easier data observation, we produced a simulated dataset including both control and treatment groups. In the table, yij is the weight of each individual mice (mousenumber) at each timepoint (obs).

```{r}
mousedata
```

In the next table, we calculate the means (yij), standard deviation (sd), and standard error (se) of the weight of all the mice at each timepoint (obs) from each treatment group (tx).

```{r}
table
```

The first graph shows the weights of individual mice during the experiment, with color differntiating treatment groups. We can see that the individuals from treatment A (control) are fairly spread out, with movement of weight having no noticable direction. However, in treatment B (treatment), we can see a visible downward direction in the movement of the lines.

```{r}
graphy1
```

The next graph is made by calculating the mean and the standard error of means of each treatment group at each timepoint. The graph's error bars shows us the standard error of means of each treatment group at each timepoint. We can see that at the first timepoint, both the mean and the error bars are fairly similar, with overlap of the bars occuring. As the experiment goes on, the means visually drift apart and the error bars become separated.

```{r}
graphy5
```

Before analysis, we checked whether the treatment A group (control) is truely normal. In order to do so, we used linear regression on the data pertaining only to treatment A. By doing so, we developed q-q plots, which is the following graph. Looking at the graph, we are able to see that, other than 2 outliers, the distribution of the points of treatment A is normal, which is what we assumed when simulating the data.

```{r}
qqPlot(model, distribution="norm", main="QQ Plot")
```

We did a simple t-test analysis. In doing so, we observe the p-values of those between complimentary treatment timepoints: 1A-1B, 2A-2B, 3A-3B, and 4A-4b. 1A-1B pertains to the first timepoint, 2A-2B to the second timepoint, and so on. By looking at these, we see that the p-value of 1A-1B is 0.9996832, 2A-2B is 0.9924810, 3A-3B is 0.1371564, and 4A-4b is 0.0352388. This tells us that at the first timepoint, the samples are the same. However, as time goes on, the differences between the two groups become more significant.

```{r}
TukeyHSD(tempanova1, conf.level = 0.95)
```



















































